AFQ-Insight

### 2019-12-01 reports/manuscript/sections/methods.tex
Removes todo list already addressed.

\subsubsection*{Categorical $y$}
When the phenotypical target variable is categorical, as in the case of
explaining or predicting the presence of a clinical diagnosis, the SGL is
readily adapted to logistic regression, where the probability of a target
variable belonging to an arbitrary defined ``true'' class is the logistic
function of the result of the linear model,

>>>>

\subsubsection*{Classification of categorical $y$}
When the phenotypical target variable is categorical, as in the case of
explaining or predicting the presence of a clinical diagnosis, the SGL is
readily adapted to logistic regression, where the probability of a target
variable belonging to an arbitrary defined ``true'' class is the logistic
function of the result of the linear model,
